cardinalR: Generating interesting high-dimensional data structures

### 2025-04-26 paper-cardinalR.Rmd
Updated the final para intro
Added datasets description table

The paper is organized as follows. In next section, introduces the implementation of `cardinalR` package on CRAN and GitHub, including demonstration of the package's key functions. We illustrate how a clustering data structure affect the Non-linear dimension reductions in **Example** section. Finally, we give a brief conclusion of the paper and discuss potential opportunities for use of our data collection.

@@

```{r}
datasets_tb <- tibble(dt = c("mobius_clust_data", 
                             "mobius_clust_tsne_param1", 
                             "mobius_clust_tsne_param2",
                             "mobius_clust_tsne_param3",
                             "mobius_clust_umap_param1",
                             "mobius_clust_umap_param2",
                             "mobius_clust_umap_param3"), 
                      text = c("",
                               "", 
                               "",
                               "",
                               "",
                               "", 
                               ""))
```

>>>>

The paper is organized as follows. In next section, introduces the implementation of `cardinalR` package on CRAN and GitHub, including demonstration of the package's key functions. We illustrate how a clustering data structure affect the dimension reductions in **Application** section. Finally, we give a brief conclusion of the paper and discuss potential opportunities for use of our data collection.

@@

```{r}
datasets_tb <- tibble(dt = c("mobiusgau", 
                             "mobiusgau_tsne1", 
                             "mobiusgau_tsne2",
                             "mobiusgau_tsne3",
                             "mobiusgau_umap1",
                             "mobiusgau_umap2",
                             "mobiusgau_umap3"), 
                      text = c("Simulated data with a Mobius and a Gaussian in 4-D space.",
                               "The tSNE embedding with perplexity 15 for mobiusgau.", 
                               "The tSNE embedding with perplexity 30 for mobiusgau.",
                               "The tSNE embedding with perplexity 5 for mobiusgau.",
                               "The UMAP embedding with number of neighbors 15 and minimum distance 0.1 for mobiusgau.",
                               "The UMAP embedding with number of neighbors 30 and minimum distance 0.08 for mobiusgau.", 
                               "The UMAP embedding with number of neighbors 5 and minimum distance 0.9 for mobiusgau."))
```
